---
title: 'Assignment 3: Melvin''s Performance Anaylsis'
author: "Jingyi(Abby) Liu"
date: "9/14/2018"
output:
  pdf_document: default
  html_document: default
---

First, clean the data by transform the column 'goal' into numerical. Replace 'Y' or 'y' by 1 and replace 'N' by 0.
```{r}
setwd('/Users/liujingyi/Documents/MSBA/6211/Homework/3.0')
#Import the data
df<-read.csv("kicksfootball.csv", header = TRUE, stringsAsFactors = FALSE)
names(df) <- c('yards', 'goal', 'practiceormatch')
#Clean the data
df[df == 'Y'|df == 'y']<-1
df[df == 'N']<-0
df$goal <- as.numeric(df$goal)

```

```{r}
summary(df)
```



### Part A 
How would you describe Melvin???s overall record?
1. In general, the probability that Melvin will hit the goal. 
```{r}
P1 = (nrow(subset(df, goal == 1)))/(nrow(df))
P1 = sprintf("%.4f", P1)
paste("Probability that Melvin will hit the goal",P1)
```
2. Will the probabilty be influenced by the nature of the attempts?(practice or match?)
```{r}
#Probability that Melvin will hit the goal on a match
Pm = (nrow(subset(df, practiceormatch == 'M'& goal == 1)))/
  (nrow(subset(df, practiceormatch == 'M')))
Pm = sprintf("%.4f", Pm)
paste("Probability that Melvin will hit the goal on a match is",Pm)

#Probability that Melvin will hit the goal on a practice
Pp = (nrow(subset(df, practiceormatch == 'P'& goal == 1)))/
  (nrow(subset(df, practiceormatch == 'P')))
Pp = sprintf("%.4f", Pp)
paste("Probability that Melvin will hit the goal on a practice is",Pp)
```
Melvin's rate of success on a practice is sligtly higher than that on a game.

3. Explore how the probability is influenced by the distance.
```{r}
Yards=seq(18,62,by=1)
Prab=rep(0,length(18:62))
#Output the probility of 'Y' under each 'yards'
for (i in 18:62) {
  a = subset(df, yards == i)
  Prab[i] = (nrow(subset(a, goal == 1)))/(nrow(a))
}
data.frame(Yards, Prab[18:62])

```
In general, with the increasement of 'yards', the probability that Melvin will hit the goal decreased.
```{r}
# Visualize the relationship between yards and probability of scoring
plot(Yards, Prab[18:62], type="l",
     xlab="yards",
     ylab="Prob(Y)",
     col="blue",lwd=2)
```

### Part B 
.Write out the logistic function for:
(1)Practices

The logistic function for practice =  log (P(y=1)/(1???P(y=1))) =b0+b1x,
For our equation b0 = 5.58180 and b1 = -0.10672.
```{r}
#Select all the practice
df_p = subset(df, practiceormatch == 'P')

# fit a logistic regression model
practice.log = glm(goal ~ yards, data=df_p,
             family=binomial)

#See the results contained in goal.log
summary(practice.log)

```
```{r}
# plot with yards on x-axis and sccoring or not (0 or 1) on y-axis
plot(goal~yards,data=df_p,
     xlab="yards", ylab="Probability of scoring on a practice")
curve(predict(practice.log, data.frame(yards=x),
              type="resp"),
      add=TRUE)
```
(2)Matches

The logistic function for practice =  log (P(y=1)/(1???P(y=1))) =b0+b1x,
For our equation b0 = 6.83393 and b1 = -0.14147 .
```{r}
#Select all the match
df_m = subset(df, practiceormatch == 'M')

# fit a logistic regression model
match.log = glm(goal ~ yards, data=df_m,
             family=binomial)

#See the results contained in goal.log
summary(match.log)
```

```{r}
# plot with yards on x-axis and sccoring or not (0 or 1) on y-axis
plot(goal~yards,data=df_m,
     xlab="yards", ylab="Probability of scoring on a match")
curve(predict(match.log, data.frame(yards=x),
              type="resp"),
      add=TRUE)
```
b) What is the probability of Melvin scoring a goal when he kicks from 20, 40 and 60 yards in
practice?
Answer:The probabilities are 0.9692, 0.7880 and 0.3054
```{r}
inp <- c(20,40,60)

newdata = data.frame(yards=inp)

predict(practice.log, newdata, type="response")
```
c) What is the probability of Melvin scoring a goal when he kicks from 20, 40 and 60 yards in
matches?
Answer:The probabilities are 0.9821, 0.7641 and 0.1605
```{r}
inp <- c(20,40,60)
newdata = data.frame(yards=inp)

predict(match.log, newdata, type="response")
```

### Part C
Plot the logistic models
```{r}
library(ggplot2)

yards_ <- c(18:62)
Probability = predict(practice.log, data.frame(yards=c(yards_)), type="response")
P_match = predict(match.log, data.frame(yards=c(yards_)), type="response")

df1 <- data.frame(yards_,Probability )
g <- ggplot(df1)
g <- g + geom_line(aes(x=yards_,y=Probability ,color='practice'))
g <- g + geom_line(aes(x=yards_,y=P_match,color='match'))
print(g)
```























