sww---
title: "A06"
author: "Jingyi(Abby) Liu"
date: "2018/10/3"
output: html_document
---

```{r}
getwd()
```
Clean the data

1. Read the traning and testing data as dataframes
```{r}
train <- read.csv("train.csv",header = TRUE)
test <- read.csv("test.csv",header = TRUE)
```
2.Dummy var the column Product_Info_2
```{r}
train$Product_Info_2_char = as.factor(substr(train$Product_Info_2, 1,1))
train$Product_Info_2_num = as.factor(substr(train$Product_Info_2, 2,2))
test$Product_Info_2_char = as.factor(substr(test$Product_Info_2, 1,1))
test$Product_Info_2_num = as.factor(substr(test$Product_Info_2, 2,2))
```


3. Delete the columns with null value rows larger than 10000
```{r}
train1 <- subset(train, select = -c(Product_Info_2, Employment_Info_6, Insurance_History_5, Family_Hist_2,Family_Hist_3,Family_Hist_4,Family_Hist_5,  Medical_History_10, Medical_History_15, Medical_History_24, Medical_History_32) )
```
4. Omitting the rows with null value
```{r}
train1[train1==""]  <- NA    
sapply(train1, function(x) sum(is.na(x)) )
```

```{r}
trainnm <- na.omit(train1)
```
```{r}
sum(is.na(trainnm))
```


5. Conbime the similar columns

(1)Combine all the columns with medical history
```{r}
Medical_Histrory <- rowSums(trainnm[,32:68])
trainnm$Medical_Histrory <- Medical_Histrory
Data_train <- trainnm[,-c(32:68)]

```
(2)Combine all the columns with medical keywords
```{r}
Medical_Keywords <- rowSums(Data_train[,32:79])
Data_train$Medical_Keywords <- Medical_Keywords
Data_train  <- Data_train [,-c(32:79)]
```

Explore the data
(1)Make the factors
```{r}
Data_train$Response <- as.factor(Data_train$Response)
```



(2)Nature of the data
```{r}
table(Data_train$Product_Info_1)
table(Data_train$Product_Info_2_char)
table(Data_train$Product_Info_2_num)
summary(Data_train$Ins_Age)
summary(Data_train$Ht)
summary(Data_train$Wt)
summary(Data_train$BMI)
summary(Data_train$Employment_Info_1)
summary(Data_train$InsuredInfo_4)
##summary(Data_train$Medical_Histrory)
summary(Data_train$Medical_Keywords)

```




```{r}
library(ggplot2)
library(GGally)
library(MASS)
library(car)
library(nnet)
```
Plot

(1) Plot the hisgram of the target 'Response'
```{r}
g <- ggplot(data = Data_train, aes(Response, fill = Response)) +
  geom_bar() +
  scale_fill_discrete(name="Response", labels=c("1", "2",'3','4','5','6','7','8')) +
  scale_x_discrete(breaks=c("1", "2",'3','4','5','6','7','8'),
                   labels=c("1", "2",'3','4','5','6','7','8'))
g
```
(2)plot the variable Product_Info_2_char
```{r}
g <- ggplot(data = Data_train, aes(Product_Info_2_char, fill = Product_Info_2_char)) +
  geom_bar() +
  scale_fill_discrete(name="Product_Info_2_char", labels=c("A", "B", 'C', 'D' ,'E')) +
  scale_x_discrete(breaks=c("A", "B", 'C', 'D' ,'E'),
                   labels=c("A", "B", 'C', 'D' ,'E'))
g
```

(3)Multicollinearity should be examined. 

From the following plots, multicollinearity exists between Weight and BMI, however, it is not very significant. 
```{r}
X <- subset(Data_train,select= c(Ht, Wt, BMI)) 
ggpairs(X)
```



```{r}
ggplot(Data_train, aes(InsuredInfo_1)) + geom_bar(aes(fill=factor(Response)))
```

```{r}
ggplot(Data_train, aes(x=Wt, y=Response,color = Response )) + geom_point(size=3,shape=21)
```

```{r}
ggplot(Data_train, aes(x=Ins_Age, y=Response,color = Response )) + geom_point(size=3,shape=21)
```

```{r}
library(dplyr)
df.train <- select(Data_train, select = -c(Id))
head(df.train)
```

```{r}
mod_log_Ius <- multinom(formula = Response ~ ., data = df.train, MaxNWts = 7000)
```

```{r}
test1 <- subset(test, select = -c(Product_Info_2, Employment_Info_6, Insurance_History_5, Family_Hist_2,Family_Hist_3,Family_Hist_4,Family_Hist_5,  Medical_History_10, Medical_History_15, Medical_History_24, Medical_History_32) )
```

```{r}
test1[test1==""]  <- NA    
sapply(test1, function(x) sum(is.na(x)) )
```
```{r}
md_test <- test1$Medical_History_1
md_test <- na.omit(md_test)
mean(md_test)
```
```{r}
 test1[is.na(test1)]<- mean(md_test)
```

```{r}
sum(is.na(test1))
```
```{r}
Medical_Histrory_Test <- rowSums(test1[,32:68])
test1$Medical_Histrory <- Medical_Histrory_Test
Data_test <- test1[,-c(32:68)]
```

```{r}
Medical_Keywords_Test <- rowSums(Data_test[,32:79])
Data_test$Medical_Keywords <- Medical_Keywords_Test
Data_test  <- Data_test [,-c(32:79)]
```


```{r}
df.test <- subset(Data_test, select = -c(Id))
```


```{r}
model.fitted <- predict(mod_log_Ius, df.test)
```

```{r}
predicted <- data.frame(test$Id)
predicted$Response <- model.fitted
names(predicted)[names(predicted)=="test.Id"]="Id"
```

```{r}
write.csv(predicted, file = 'predicted.csv', row.names = FALSE)
```


